QPLIB: A Library of Quadratic Programming Instances

### 2016-07-19 QPLIB.tex
Nikolaos Sahinidis' comments on the abstract

\title{QPLIB: a Library of a Quadratic Programming Instances}

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP). QP is a very ``varied'' class, comprising sub-classes of problems ranging from trivial to indecidable. Correspondingly, solution methods for QP are very diverse, ranging from entirely combinatorial ones to completely continuous ones, to many where both aspects are fundamental. Selecting a set of instances of QP that is at the same time not overwhelmingly numerous and significant for the many different interested communities is therefore challenging. In order to help our selection process we propose a simple taxonomy for QP instances. We then briefly survey the field of QP, giving an overview of theory, methods and solvers. Finally we describe how the library was put together, and how the final results look.
\end{abstract}

>>>>

\title{QPLIB: A Library of Quadratic Programming Instances}

@@

\begin{abstract}
 This paper describes a new instance library for Quadratic Programming (QP). QP is a very ``varied'' class, comprising sub-classes of problems ranging from trivial to undecidable. Solution methods for QP are very diverse, ranging from entirely combinatorial ones to completely continuous ones, to many where both aspects are fundamental. Selecting a set of instances of QP that is at the same time not overwhelmingly difficult and sufficiently challenging for the many different interested communities is therefore important. 
 %In order to help our selection process 
 We propose a simple taxonomy for QP instances that leads to a systematic problem selection mechanism. We then briefly survey the field of QP, giving an overview of theory, methods and solvers. Finally we describe how the library was put together, and detail its final contents.
\end{abstract}
